Blocking-resistant communication\\through domain fronting

### 2014-07-17 docs/meek.tex
Make the traffic characteristic graphs fit again.
Still need some work.
Fix some wording.

\begin{abstract}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Fronting enables a communication stream that is apparently with an allowed domain,
but actually with a forbidden domain.
The technique uses different domain names are used in different
parts of an HTTP request.
One domain is used on the ``outside''---in the DNS request and
TLS Server Name Indication---while another domain is used
on the ``inside''---the HTTP Host header, invisible to the
censor under HTTPS encryption.
A variety of difficult-to-block web services, such as content delivery networks
and Google App Engine, ignore the outside of an HTTPS request
and dispatch it internally according to the Host header:
their frontend servers effectively provide a front,
behind which any domain on their network may be accessed
without revealing the destination to the censor.
If a censor is unable to identify which traffic is fronted,
then blocking the traffic means blocking a content delivery network wholesale,
with resulting expensive collateral damage.
Fronting has been used successfully for a few years by a circumvention system called GoAgent;
we provide a systematic examination of its potential and limitations,
and the results of building an implementation.

@@

\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{figs/datalen-google-cdf.png}
\caption{Normal Google Traffic}
\label{fig:len:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{figs/datalen-tbb-cdf.png}
\caption{Traffic Using meek}
\label{fig:len:meek}
\end{subfigure}

\caption{TCP packet payload size distribution}
\label{fig:len}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.7\textwidth, angle=270]{figs/connections-google.eps}
\caption{Histogram of each user's connections in the 10-minute window}
\label{fig:connections}
\end{figure}
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{figure}
\centering
\includegraphics[width=0.8\textwidth]{figs/conns.eps}
\caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
\label{fig:conconns}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-google-cdf.eps}
\caption{Normal Google Traffic}
\label{fig:duration:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
\caption{Traffic Using meek (Notice the x-axis)}
\label{fig:duration:meek}
\end{subfigure}

\caption{Connection lifetime distribution}
\label{fig:duration}
\end{figure}

>>>>

\begin{abstract}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Fronting enables a communication stream that is apparently with an allowed domain,
but actually with a forbidden domain.
The technique uses different domain names at different communication layers.
One domain is used on the ``outside''---in the DNS request and
TLS Server Name Indication---while another is used
on the ``inside''---the HTTP Host header, invisible to the
censor under HTTPS encryption.
A variety of difficult-to-block web services, such as content delivery networks
and Google App Engine, ignore the outside of an HTTPS request
and dispatch it internally according to the Host header:
their frontend servers effectively provide a front,
behind which any domain on their network may be accessed
without revealing the destination to the censor.
If a censor is unable to identify which traffic is fronted,
then blocking the traffic means blocking a content delivery network wholesale,
with resulting expensive collateral damage.
Fronting has been used successfully for a few years by a circumvention system called GoAgent;
we provide a systematic examination of its potential and limitations,
and the results of building an implementation.

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{figs/datalen-google-cdf.png}
\caption{Normal Google Traffic}
\label{fig:len:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[width=\textwidth]{figs/datalen-tbb-cdf.png}
\caption{Traffic Using meek}
\label{fig:len:meek}
\end{subfigure}

\caption{TCP packet payload size distribution}
\label{fig:len}
\end{figure*}

@@

\begin{figure}
\centering
\includegraphics[height=\linewidth, angle=270]{figs/connections-google.eps}
\caption{Histogram of each user's connections in the 10-minute window}
\label{fig:connections}
\end{figure}
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{figure}
\centering
\includegraphics[width=\linewidth]{figs/conns.eps}
\caption{Concurrent HTTPS connections over time. We measure the trace for the Tor Browser Bundle and Firefox/Chrome extensions.}
\label{fig:conconns}
\end{figure}

@@

\begin{figure*}
\centering
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-google-cdf.eps}
\caption{Normal Google Traffic}
\label{fig:duration:lbl}
\end{subfigure}%
%add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc.
%(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.5\textwidth}
\includegraphics[height=\textwidth, angle=270]{figs/flowduration-tbb-cdf.eps}
\caption{Traffic Using meek (Notice the x-axis)}
\label{fig:duration:meek}
\end{subfigure}

\caption{Connection lifetime distribution}
\label{fig:duration}
\end{figure*}
